Preregistration analysis, Cost 2 study

### 2019-09-19 Cost2/Cost2_prereg.Rmd
small aesthetic changes to plots

autoplot(survData) +
  geom_vline(xintercept = 1, lty = 2) + # end of the grace period for physical trials
  scale_color_manual(values = cols) +
  scale_fill_manual(values = cols) +
  scale_x_continuous(breaks = seq(14)) +
  ylim(0, 1) +
  labs(x = "Time in Trial", y = "Proportion Completed", fill = "Cost", color = "Cost") +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.line = element_line(colour = "black"),
        text = element_text(size = 16))

>>>>

autoplot(survData) +
  geom_vline(xintercept = 1, lty = 2) + # end of the grace period for physical trials
  scale_color_manual(values = cols) +
  scale_fill_manual(values = cols) +
  scale_x_continuous(breaks = seq(14)) +
  ylim(0, 1) +
  labs(x = "Time in Trial", y = "Proportion Accepted", fill = "Cost", color = "Cost") +
  theme(legend.position = c(0.3, 0.2),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.line = element_line(colour = "black"),
        text = element_text(size = 22))
